---
title: "Plotly"
author: "Maulid Hussein Bwabo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intsructions
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 
# Research questions 
The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you’re grading this assignment?
2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Installing packages
```{r}
#Plotly package
install.packages("plotly",repos = "http://cran.us.r-project.org")
library(plotly)
```

```{r}
plot_ly(z=volcano, type="surface")
```